---
title: "Curriculum vitæ"
---

## {{< fa briefcase >}} Professional experience 
```{r}
#| echo: false
#| results: asis

data <- openxlsx::read.xlsx("CV.xlsx",sheet = "Experience")
data[is.na(data[,"Lieu_en"]), "Lieu_en"] <- data[is.na(data[,"Lieu_en"]), "Lieu"]
data[is.na(data[,"Date_en"]), "Date_en"] <- data[is.na(data[,"Date_en"]), "Date"]

for (i in 1:nrow(data)) {
  date <- data[i, "Date_en"]
  intitule <- data[i, "Intitulé_en"]
  lieu <- data[i, "Lieu_en"]
  cat(":::: {.columns}\n")
  cat("::: {.column width=\"10%\"}\n")
  cat(date, "\n")
  cat(":::\n")
  cat("::: {.column width=\"90%\"}\n")
  cat(gsub("\\.\\.", ".", sprintf("**%s**, %s.\n", intitule, lieu)))
  cat(":::\n")
  cat("::::\n\n")
}
```

## {{< fa user-graduate >}} Education 

:::: {.columns}
::: {.column width="10%"}
2020 -
:::
::: {.column width="90%"}
**PhD Student at [EDGE](https://ed-edge.doctorat-bretagneloire.fr), Nantes Atlantique Economics and Management Laboratory ([LEMNA](https://lemna.univ-nantes.fr){target="_blank"})**.

- Real-time detection of turning points: contribution of the use of asymmetric filters in business cycle analysis.  
- Under the supervision of Olivier Darné (LEMNA) and Dominique Ladiray (Insee). 
:::
::::

:::: {.columns}
::: {.column width="10%"}
2019 - 2021
:::
::: {.column width="90%"}
**National School of Statistics and Economic Administration** ([ENSAE](https://www.ensae.fr/en){target="_blank"}).
:::
::::

:::: {.columns}
::: {.column width="10%"}
2014 - 2015
:::
::: {.column width="90%"}
**Master of Science in statistics-econometrics, specialisation in official statistics and statistical studies**, [ENSAI](http://ensai.fr/fr){target="_blank"} 
/ [Université Rennes 1](https://math.univ-rennes1.fr){target="_blank"}.
:::
::::

:::: {.columns}
::: {.column width="10%"}
2013 - 2014
:::
::: {.column width="90%"}
**Bachelor of Economics in Science of organizations and markets, applied economics**, [Université Paris-Dauphine](https://dauphine.psl.eu/en/formations/licences/economie-appliquee){target="_blank"}.
:::
::::

:::: {.columns}
::: {.column width="10%"}
2012 - 2013
:::
::: {.column width="90%"}
**Bachelor of Science in Mathematics equivalent**,
[Université Rennes 1](https://math.univ-rennes1.fr/licence-mention-mathematiques){target="_blank"}.
:::
::::


:::: {.columns}
::: {.column width="10%"}
2012 - 2014
:::
::: {.column width="90%"}
**National School for Statistics and Information Analysis, France**   ([ENSAI](http://ensai.fr/en){target="_blank"}).
:::
::::

:::: {.columns}
::: {.column width="10%"}
2010 - 2012
:::
::: {.column width="90%"}
**Post-secondary preparatory school in Mathematics, Physics and Computer Science (France's Grandes écoles)**, [Lycée Carnot](http://lyc21-carnot.ac-dijon.fr){target="_blank"}, Dijon.
:::
::::



## {{< fa newspaper >}} Publications / Interventions

### Publications

```{r}
#| echo: false
#| results: asis

data <- openxlsx::read.xlsx("CV.xlsx",sheet = "Publications")
data[is.na(data$Title), "Title"] <- paste(data[is.na(data$Title), "Titre"], "(French article)") 
for (i in 1:nrow(data)) {
  titre <- sprintf("* %s.", data[i,"Title"])
  titre <- gsub("\\.\\.", ".", titre)
  resume <- data[i,"Summary"]
  cat(titre, "\n\n")
  if( !all(is.na(resume))) {
    cat("::: {.callout-resume .callout-warning collapse=true}\n")
    cat("### Summary\n")
    cat(resume, "\n")
    cat(":::\n\n")
  }
}
```


**Reviewer for the journals** : [Statéco](https://www.insee.fr/en/information/2116798){target="_blank"},
_[Journal of Official Statistics](https://www.scb.se/jos){target="_blank"}_,
_[Statistical Journal of the IAOS](https://officialstatistics.com){target="_blank"}_, 
_[International Journal of Operational Research](https://www.inderscience.com/jhome.php?jcode=ijor){target="_blank"}_, _[The R journal](https://journal.r-project.org){target="_blank"}_.

### Interventions


- {{< fa brands r-project >}} package `tvCoef`, implementing time-varying coefficients models has never been so easy (2023), [Workshop on Time Series Analysis and Statistical Disclosure Control Methods for Official Statistics](https://aqlt.github.io/slides/2023%20-%2012%20-%20OECD/Slides.pdf){target="_blank"}.

- With Abbas R., Carnot N., Lequien M., Roux S., L'effet macro-économique de la transition bas carbone (2023), Séminaire D2E.

- Manipuler les moyennes mobiles avec R et JDemetra+ (2023), [Rencontres R](https://aqlt.github.io/slides/2023%20-%2006%20-%20Rencontres%20R/Slides_rr.pdf){target="_blank"}.

- With [du Campe de Rosamel C.](https://www.linkedin.com/in/claire-de-rosamel-61a046202/) (6-month internship), Utilisation de modèles de régression à coefficients variant dans le temps pour la prévision conjoncturelle (2023), [Atelier D2E](https://aqlt.github.io/AteliertvCoef/){target="_blank"}.


- R and JDemetra+ 3.0: A new toolbox around seasonal adjustment and time series analysis (2022), [2nd Workshop on Time Series Methods for Official Statistics](https://aqlt.github.io/slides/2022%20-%2009%20-%20OECD/Slides_AQLT.pdf){target="_blank"}, [uRos](https://aqlt.github.io/slides/2022%20-%2011%20-%20uRos/Slides_AQLT.pdf){target="_blank"}.

- Trend-cycle extraction and moving average manipulations in R with the rjdfilters package (2022), [4th Seasonal Adjustment Practitioners Workshop](https://aqlt.github.io/slides/2022%20-%2006%20-%20SAPW/Slides_AQLT.pdf){target="_blank"}.

- Estimation en temps réel de la tendance-cycle : Apport de l'utilisation des filtres asymétrique (2022), [1ère Journée d'Économétrie Appliquée « Michel TERRAZA »](https://aqlt.github.io/slides/2022%20-%2005%20-%20JEAMT/Slides_AQLT.pdf){target="_blank"}.

- Performance of asymmetric filters for trend-cycle extraction - Application to the COVID-19 crisis (2021), [JSM (2021)](https://ww2.amstat.org/meetings/jsm/2021/onlineprogram/AbstractDetails.cfm?abstractid=317462){target="_blank"}.

- Performance of asymmetric filters for trend-cycle extraction - Application to the COVID-19 crisis (2021), [New Techniques and Technologies for Statistics  (NTTS)](https://aqlt.github.io/slides/2021%20-%2003%20-%20NTTS/Slides.pdf){target="_blank"}.

- Leading and participating in a Hackathon on RJDemetra (two days, 2019), Deutsche Bundesbank, Francfort.

- RJDemetra: an R interface to JDemetra+ (2019), [Seasonal Adjustment Center of Excellence (SACE) Meeting #6](https://aqlt.github.io/slides/2019%20-%2003%20-%20SAEG%20and%20SAUG/rjdemetra_saeg.pdf), [New Techniques and Technologies for Statistics  (NTTS)](https://aqlt.github.io/slides/2019%20-%2003%20-%20NTTS/rjdemetra.pdf){target="_blank"}, Seasonal Adjustment Expert Group (SAEG), [useR!2019](http://user2019.r-project.org/static/pres/t256274.pdf){target="_blank"}.

- Ladiray D. et Quartier-la-Tente A. (2019), (In)Stability of Reg-ARIMA Models for Seasonal Adjustment, *[New Techniques and Technologies for Statistics  (NTTS)](https://aqlt.github.io/slides/2018%20-%2009%20-%20SACE/RegARIMA%20estimation/2018-10-04%20(In)Stability%20of%20Reg-Arima%20Estimations.pdf){target="_blank"}*.

- R and JDemetra+: RJDemetra and rjdqa (2018), [Seasonal Adjustment Center of Excellence (SACE) Meeting #5](https://aqlt.github.io/slides/2018%20-%2009%20-%20SACE/R%20and%20JD%2B/rjdemetra.pdf).


## {{< fa chalkboard-teacher >}} Trainings 


:::: {.columns}
::: {.column width="10%"}
2022-
:::
::: {.column width="90%"}
**Trainer on time series analysis with R**
(12h),
[CEPE](https://www.lecepe.fr/formations/methodes-statistiques/series-temporelles/analyse-des-series-temporelles-avec-r_44.html){target="_blank"}, Paris.
:::
::::

:::: {.columns}
::: {.column width="10%"}
2021-2022
:::
::: {.column width="90%"}
**Lecturer in time series analysis**, [ENSAE](https://www.ensae.fr/en){target="_blank"},
Paris.
:::
::::


:::: {.columns}
::: {.column width="10%"}
2021
:::
::: {.column width="90%"}
**Seasonal with JDemetra+ et RJDemetra**
(24h), RTE, Paris.
:::
::::


:::: {.columns}
::: {.column width="10%"}
2019-
:::
::: {.column width="90%"}
**Trainer on seasonal and working days adjustment (SA-WDA)**
(24h),
[CEPE](https://www.lecepe.fr/formations/methodes-statistiques/series-temporelles/desaisonnaliser-une-serie-temporelle_42.html){target="_blank"}, Paris.
:::
::::

:::: {.columns}
::: {.column width="10%"}
2017 - 2019
:::
::: {.column width="90%"}
**Trainer on seasonal and working days adjustment (SA-WDA)**,[INSEE](https://www.insee.fr/en){target="_blank"},
Paris.
:::
::::


:::: {.columns}
::: {.column width="10%"}
2016
:::
::: {.column width="90%"}
**Lecturer in introduction to the statistical software {{< fa brands r-project >}}**, [ENSAE](https://www.ensae.fr/en){target="_blank"},
Paris.
:::
::::


## {{< fa globe-europe >}} Cooperations

```{r}
#| echo: false
#| results: asis

data <- openxlsx::read.xlsx("CV.xlsx",sheet = "Cooperations")
data$Descriptif_en <- gsub("\\.\\.", ".", paste0(data$Descriptif_en,"."))
for (i in 1:nrow(data)) {
  annee <- data[i, "Année"]
  pays <- data[i, "Lieu_en"]
  descriptif <- data[i, "Descriptif_en"]
  cat(":::: {.columns}\n")
  cat("::: {.column width=\"15%\"}\n")
  cat(sprintf("**%s** (%s)\n", pays, annee))
  cat(":::\n")
  cat("::: {.column width=\"85%\"}\n")
  cat(descriptif, "\n")
  cat(":::\n")
  cat("::::\n\n")
}
```
